{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-13 paper/paper.tex
corrected wording

These instructions are not further specified, but contain an instruction
to start a new thread (\texttt{start \textit{pc}} where pc is the start
instruction of the new thread).

>>>>

These instructions are not further specified, but contain an instruction
to create a new thread (\texttt{start \textit{pc}} where pc is the start
instruction of the new thread).
